The goal of this project is to design and implement a small-scale free and open-source software solution for stock management. This solution should provide an easy to use platform for small businesses or organizations that need to manage stocks.

When looking for the definition of stock in, for example, the Merriam-Webster dictionary, the first definition that can be found reads “the supply of goods available for sale in a store” \cite{1}. Although this is a good enough definition, for this project it is better to draw upon the next one, which defines a stock as “a supply of something that is available for use”. Therefore, this project aims to provide a solution for any potential user that needs to manage a supply.

\subsection{Glossary}
Following is a basic list of important terms in the context of this project:

\begin{labeling}{Community member}
\item[\textbf{Customer}]{An entity which consumes (usually buys) goods.}
\item[\textbf{Provider}]{An entity which provides (usually sells) goods.}
\item[\textbf{POS}]{Point of sale. A platform or device used to complete and process a sale.}
\item[\textbf{Stock}]{A supply of something that is available for use.}
\item[\textbf{Stock management}]{(excerpt from The Business Dictionary) The administrative role of assessing the inventory of a business and making sure it is sufficient to meet consumer demand \cite{3}.}
\end{labeling}

\subsection{Stakeholders}
Following are the different stakeholders related to the development, implementation and use of the product, with a description of their roles and functions:

\begin{labeling}{Community member}
\item[\textbf{Product owner}]{Acts as the promoter of the product. Sets the requirements of the product and has the last word regarding its features and functionalities.}
\item[\textbf{Developer}]{Member of the official core team of development. (For this particular project, it will be the same person as the product owner)}
\item[\textbf{Contributor}]{Any developer of the community that submits a contribution to the source code that is accepted.}
\item[\textbf{Community member}]{Any member of the community related to the product that collaborates in any way towards the goal of the project (i.e. reporting a bug, suggesting improvements, giving feedback…)}
\item[\textbf{User}]{The final consumer of the product. This actor has management needs over a particular stock and therefore uses and profits from the product.}
\end{labeling}