Following the identification of the resources and their costs, a budget estimation can be elaborated taking into account the usage of every resource. The free resources and the resources with no associated cost will be ignored, as the budget only needs to take into account the economical aspect.

In the case of this project, as explained in the scope and contextualization section, the Product owner and the Core developer will be the same person, with some of the functions of each role being tightly coupled with the ones from the other role. Thus a rough estimation of the different participation has been elaborated.

The total cost in hours for this person is of 420 hours, and it includes the tasks for both roles. Slight variations might occur, but based on the evolution of the project, the estimation can be considered precise enough.
\hfill\break
\begin{center}
    \begin{tabular}{ | l | l | l | r |}
    	\hline
 		\textbf{Resource} & \textbf{Cost} & \textbf{Unit} & \textbf{Total} \\ \hline
 		Product owner & 20.00\euro{}/hour & 120 hours & 2400.00\euro{} \\ \hline
 		Core developer & 16.00\euro{}/hour & 300 hours & 4800.00\euro{} \\ \hline
 		Acer Aspire 5735 & 499.90\euro{} & 3\% * & 14.97\euro{} \\ \hline
 		Custom dektop PC & 1100.00\euro{} & 12.5\% ** & 137.50\euro{} \\ \hline
 		PHPStorm & 159.00\euro{}/year & 20\% *** & 38.10\euro{} \\ \hline
 		Microsoft Word & 149.00\euro{} & 20\% *** & 29.80\euro{} \\ \hline
 		DigitalOcean Droplet & 5.40\euro{}/month & 33\% **** & 1.78\euro{} \\ \hline
 		\textbf{Resource} &  &  & \textbf{7422.15\euro{}} \\ \hline
    \end{tabular}
\end{center}
\hfill\break
{\tiny \textbf{*} Computer used during 8 years. Used during 6 months because of the project, and half of its use is directly related to the project. This yields a rough 3\% usage.}

{\tiny \textbf{**} Computer used during 2 years. Used during 6 months because of the project, and half of its use is directly related to the project. This yields a rough 12.5\% usage.}

{\tiny \textbf{***} Software used for other projects. The 20\% usage is an estimated approximation that takes into account other projects that share the cost of the program, and cannot be disclosed in this budget.}

{\tiny \textbf{****} The service is shared with other ongoing projects. The 33\% usage is an estimated approximation that takes into account other ongoing projects that share the cost of the platform, and cannot be disclosed in this budget.}