Having researched on this area, the conclusion is that with the huge amount of existing solutions, it is hard to find a use case that is not already fully covered. Even with free and open-source solutions, the options, although quite limited \cite{4,5} in the free version or technically speaking \cite{6}, are many.

However, there seems to be a lack in a particular area. All of these solutions are quite rigid and platform specific. They are not easily portable or extendable. There is no solution in the form of an open-source API for basic inventory management, so the goal of this project is to cover this need with a solution that follows this model.

In a similar way, one of the main goals of this project is for it to be free and opensource. The users and clients won't have to pay in order to install and use the software. Support for the software will come from the community that forms around the product, and extra features and extensions of the service and the platform will be done by voluntary contributors.

The solution has to be easy to install and use so the service will be designed as a lightweight standalone solution so it can be installed on a single computer with average specifications and served through a local network. The advantage of this is that a client will not need any additional hardware or software dependencies or integrations, and so the usage of the service will not mean any additional costs.

Another one of the main goals of this service is also to be easily extendable so clients with custom and different needs can implement additional logics and features.

This project will potentially have a positive impact as it would potentially become a critical platform for the improvement of small businesses and companies that decide to adopt it. While not incurring in extra costs for the users and while not representing a noticeable imprint on the environment in any aspect, it can mean a huge improvement in the efficiency and profit for small users and companies that lack this kind of solution and otherwise could not afford such a system.