The first step for the elaboration of a budget is to clearly identify the associated costs for every task and resource involved in the project. The goal of the budget is to allow to decide if the project is feasible and makes sense from a cost perspective. The study of the costs includes both human and material resources, as well as possible unforeseen events that might affect the project.

\section{Human resources}
Following are listed the different roles that are involved in the project during the development phase, with their associated cost:
\hfill\break
\begin{center}
    \begin{tabular}{ | l | r |}
    	\hline
 		\textbf{Role} & \textbf{Estimated cost (/hour)} \\ \hline
 		Product owner & 20.00\euro{} \\ \hline
 		Core developer & 16.00\euro{} \\ \hline
    \end{tabular}
\end{center}
\hfill\break
The rest of the roles, as described on the scope and contextualization of the project, have a volunteer involvement on the project, if any, and their involvement is also considered to be after the development phase, and so they don’t represent any additional cost for the project.

\section{Material resources}
Following are listed the material resources used during the development phase of the project. These include hardware, software and licenses.
\hfill\break
\begin{center}
    \begin{tabular}{ | l | r |}
    	\hline
 		\textbf{Resource} & \textbf{Estimated cost} \\ \hline
 		Acer Aspire 5735 & 499.90\euro{} \\ \hline
 		Custom desktop PC & 1100.00\euro{} \\ \hline
 		PHPStorm & 159.00\euro{}/year \\ \hline
 		Sublime Text 2 & Free \\ \hline
 		Vim & Free \\ \hline
 		Microsoft Word 15 & 149.00\euro{} \\ \hline
 		Google Drive & Free \\ \hline
 		Google Docs & Free \\ \hline
 		GanttPro & Free \\ \hline
 		GitHub Account & Free \\ \hline
 		Trello Account & Free \\ \hline
 		DigitalOcean Droplet & 5.40\euro{}/month \\ \hline
 		Google Chrome & Free \\ \hline
 		Postman & Free \\ \hline
    \end{tabular}
\end{center}
\section{Indirect resources}
Some costs indirectly related to the project must also be taken into account. These costs usually include the internet connection, power, phone calls, transportation, etc. In the case of this project, these resources can be ignored, as they are shared for other purposes and therefore their associated cost becomes negligible.

\section{Other costs}
Usually a budget would also include a margin to cover unexpected conflicts and situations. In this project this would only make sense regarding the human resources (i.e. the analysis or development takes more time than expected), as the material resources are shared with other projects and tasks, and none of them are directly and exclusively related to this project. However, given that the human resources correspond to a student and a tightly defined schedule, any delays and conflicts will have to be covered within the specified dates. The budget can therefore be considered to be rigid regarding the hours.

The budget of this project doesn’t take into account the costs generated by the usage of this project from clients or users, once the development phase is finalised.