\begin{thebibliography}{9}

\bibitem{1}
Merriam Webster. 2016. Stock | Definition of Stock by Merriam-Webster. [ONLINE] Available at: http://www.merriam-webster.com/dictionary/stock. [Accessed 26 September 2016].

\bibitem{2}
Business Dictionary. 2016. What is stock management? definition and meaning - BusinessDictionary.com [ONLINE] Available at: http://www.businessdictionary.com/definition/stock-management.html. [Accessed 26 September 2016].

\bibitem{3}
Purchasing Procurement Center. 2016. Top 5 Principles of Inventory Management. [ONLINE] Available at: http://www.purchasing-procurement-center.com/principles-of-inventory-management.html. [Accessed 26 September 2016].

\bibitem{4}
Wikipedia. 2016. Just-in-time manufacturing [ONLINE] Available at: https://en.wikipedia.org/wiki/Just-in-time\_manufacturing. [Accessed 26 September 2016].

\bibitem{5}
Wasp Barcode. 2016. 5 Lean Inventory Principles: Ending Inventory Waste [ONLINE] Available at: http://www.waspbarcode.com/buzz/5-lean-inventory-principles/. [Accessed 26 September 2016].

\bibitem{6}
Carta. 2016. Order and Inventory Management Software System for Stock Control Carta [ONLINE] Available at: https://getcarta.com/. [Accessed 26 September 2016].

\bibitem{7}
Odoo. 2016. ERP y CRM de código abierto | Odoo [ONLINE] Available at: https://www.odoo.com/es\_ES/. [Accessed 26 September 2016].

\bibitem{8}
Almyta.com. 2016. Free ABC Inventory Software Features [ONLINE] Available at: http://almyta.com/abc\_inventory\_software.asp. [Accessed 26 September 2016].

\bibitem{9}
Scrum. 2017. Scrum (software development) - Wikipedia [ONLINE] Available at: https://en.wikipedia.org/wiki/Scrum\_(software\_development) [Accessed January 2017].

\bibitem{10}
Devcode.la. 2016. 5 frameworks de PHP requeridos en el 2016 [ONLINE] Available at: https://devcode.la/blog/5-frameworks-php-requeridos/ [Accessed January 2017].

\bibitem{11}
Laravel. 2016. Routing - Laravel - The PHP Framework For Web Artisans [ONLINE] Available at: https://laravel.com/docs/5.3/routing [Accessed December 2016].

\bibitem{12}
LaTeX. 2017. LaTeX - A document preparation system [ONLINE] Available at: https://www.latex-project.org [Accessed January 2017].

\end{thebibliography}