Following is a list of the resources which are expected to be used along the completion of the project:

\begin{addmargin}[1em]{0em}
\textbf{Acer Aspire 5735 w. Ubuntu 14.04 LTS}\\
Personal laptop, used mainly for coding on a local development environment and for documentation purposes with an auxiliary character.

\textbf{Custom-build desktop computer w. Ubuntu 14.04 LTS}\\
Personal desktop computer. This will be the main development tool. It will have a local development environment and it will also be used as the usual tool from where to deploy and manage production environments.

\textbf{PHPStorm} (\url{https://www.jetbrains.com/phpstorm})\\
PHP oriented IDE. It will be the main tool for writing and maintaining code.

\textbf{Sublime Text 2} (\url{https://sublimetext.com/2})\\
Text editor. It will mainly be used to manage documentation and configurations, more than code.

\textbf{Vim} (\url{http://www.vim.org})\\
Text editor. It will be used usually to manage configuration and possibly code on the servers and virtual machines that may be used.

\textbf{Microsoft Word 15}\\
Text processor. Used for documentation purposes.

\textbf{Google Drive} (\url{http://www.google.es/drive/apps.html})\\
Repository used for storing, managing and sharing the documentation.

\textbf{Google Docs} (\url{https://docs.google.com})\\
Used for generating documentation in a shared way.

\textbf{GanttPro} (\url{https://app.ganttpro.com})\\
Online Gantt tool for generating gantt diagrams.

\textbf{GitHub Account} (\url{https://github.com})\\
Source code repository. It allows to store and manage the source code in a public way, which is a key feature for an open-source project.

\textbf{Trello Account} (\url{https://trello.com})\\
Online tool for task management. It will be used at a personal level to keep track of ongoing tasks.

\textbf{DigitalOcean Droplet} (\url{https://digitalocean.com})\\
Server instance on which the production code will be hosted and run.

\textbf{Google Chrome} (\url{https://www.google.com/chrome})\\
The usual browser used to access internet throughout the whole project, for information purposes as well as running and using the client-side infrastructure.

\textbf{Postman} (\url{https://www.getpostman.com})\\
A REST client used for testing the use of REST APIs.
\end{addmargin}
